%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[margin=0.5in]{geometry}
\usepackage[pdftex]{hyperref}

\hypersetup{
    colorlinks = true,
    linkcolor = blue,
    urlcolor = blue
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4pt}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{%
  \item[\textbullet]\small{%
    \textbf{#1}: #2 \vspace{-2pt}%
  }%
}

\newcommand{\resumeItemWithoutTitle}[1]{%
  \item[$\bullet$]\small{#1 \vspace{-2pt}}%
}

\newcommand{\resumeSubheading}[4]{%
  \item[]%  ← keeps list structure, shows no bullet
  \vspace{-1pt}%
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}%
    \textbf{#1} & #2 \\%
    \textit{\small #3} & \textit{\small #4} \\%
  \end{tabular*}%
  \vspace{-5pt}%
}

\newcommand{\resumeHeading}[2]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{%
  \item[]\small{%
    \textbf{#1}: #2 \vspace{-2pt}%
  }%
  \vspace{-4pt}%
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{\LARGE John Perkins} &
    \href{mailto:john.mc.perkins@gmail.com}{john.mc.perkins@gmail.com} \;•\;
    \href{https://www.linkedin.com/in/johnbperkins/}{linkedin.com/in/johnbperkins} \;•\;
    480-395-9777 \\
\end{tabular*}

\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textit{Backend Software Engineer · Distributed Systems } &
    \href{https://github.com/johnbperkins}{github.com/johnbperkins}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
    \resumeHeading
      {M.S. Computer Science - Arizona State University - 3.8 GPA}{May 2025}
    
    \resumeHeading
      {B.S. Computer Science - Arizona State University - 3.47 GPA}{Dec 2023}
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
    \resumeSubItem{Languages}{Python, Go, C++, Java, Bash, SQL}
    \resumeSubItem{Frameworks / Infra}{FastAPI, gRPC, REST, WebSockets, Docker, Kubernetes, Terraform, GitHub Actions}
    \resumeSubItem{Cloud / DevOps}{AWS (ECS, ECR, SQS, RDS, ElastiCache, S3, Cognito, IAM), CI/CD, Git}
    \resumeSubItem{Data / Reliability}{Redis, PostgreSQL, MongoDB, Prometheus, Grafana, k6, Postman}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {Researcher}{Tempe, AZ}
        {School of Computing and Augmented Intelligence, ASU}{August 2023 - May 2025}
        \resumeItemListStart
            \resumeItem{Adversarial Attacks on Implicit Neural Representation Networks}
            {
            \begin{itemize}[label=-]
                \item Engineered adversarial-attack modules for INR classifier pipelines, identifying and patching key vulnerabilities.
                \item Built a gradient-approximating \textbf{surrogate model} to craft image-space attacks and benchmark defenses.
                \item Built a \textbf{Slurm/Bash} hyperparameter-tuning pipeline for \textbf{70+ parallel GPU jobs}.
    
            \end{itemize}
            }            
        \resumeItemListEnd    

    \resumeSubheading
    {Software Engineer \normalfont{\textit{(Intern)}}}{Tempe, AZ}
    {Choice Hotels International}{May 2023 - December 2023}
    \resumeItemListStart
        \resumeItem{Cross-Platform Ticket Synchronization between ServiceNow and Jira}
        {
        \begin{itemize}[label=-]
            \item Engineered an \textbf{integration system} to synchronize \textbf{300 support tickets/day} between \textbf{ServiceNow} and \textbf{Jira}.
            \item Used \textbf{Webhooks} and \textbf{JavaScript} to enable automatic bidirectional information flow in real time.
            \item Streamlined workflows to improve team collaboration, reduce errors, and dropped resolution times from \textbf{weeks to days}.
        \end{itemize}
        }
    \resumeItemListEnd

    \resumeSubheading
    {Software Engineer \normalfont{\textit{(Intern)}}}{Remote}
    {Automationtechies}{May 2022 -  August 2022}
        \resumeItemListStart
            \resumeItem{Commission Tracking System}
            {
            \begin{itemize}[label=-]
                \item Built a \textbf{Node.js ETL service} that ingests \textbf{500 rows/day} via \textbf{REST APIs}, aggregates them, and generates cloud reports; load-tested to sustain \textbf{\textgreater{}50k rows/day} for future growth.
                \item Automated reporting, cutting generation time by \textbf{90\%}.
            \end{itemize} 
            }
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart  
    \resumeHeading{\href{https://github.com/johnbperkins/chat-service}{Real-Time Chat Service}}{Go · NATS JetStream · MongoDB}
    \resumeItemListStart
        \resumeItemWithoutTitle{Built a horizontally scalable real-time chat backend using \textbf{Go WebSockets} and \textbf{NATS JetStream} for durable message distribution, supporting 1:1 and group conversations with JWT authentication.}
        \resumeItemWithoutTitle{Architected stateless backend nodes with \textbf{MongoDB} persistence and \textbf{Chi router}, enabling seamless horizontal scaling for concurrent user sessions.}
        \resumeItemWithoutTitle{Implemented WebSocket protocol with real-time typing indicators, read receipts, and cursor-based message pagination APIs.}
    \resumeItemListEnd

    \resumeHeading{\href{https://urlshortfront.vercel.app/}{URL Shortener}}{Go · gRPC · AWS · Redis · Docker · PostgreSQL}
    \resumeItemListStart
        \resumeItemWithoutTitle{Designed a high-throughput URL-shortening service with \textbf{gRPC}, \textbf{Redis} cache, and \textbf{PostgreSQL} storage; containerized with Docker.}
        \resumeItemWithoutTitle{Load-tested to \textbf{5k req/s} at \textless{}150 ms p95 latency while maintaining \textbf{99.99\% success rate}.}
        \resumeItemWithoutTitle{Implemented CI/CD with \textbf{GitHub Actions} and \textbf{Terraform}, enabling one-click rollout to \textbf{AWS}.}
    \resumeItemListEnd

    \resumeHeading{Browser Automation Agent}{Python · FastAPI · AWS · Docker · PostgreSQL}
    \resumeItemListStart
        \resumeItemWithoutTitle{Deployed \textbf{FastAPI} based \textbf{Docker} containers that orchestrate an AI-powered browser agent for dynamic web interaction.}
        \resumeItemWithoutTitle{Implemented secure user authentication with \textbf{Supabase} and \textbf{PostgreSQL} for persistent configuration and session data.}
    \resumeItemListEnd

    \resumeHeading{High-Volume  Jobs Scraper}{Python · Docker · PostgreSQL}
    \resumeItemListStart
        \resumeItemWithoutTitle{Engineered a \textbf{Playwright}-based scraper that harvested \textbf{100k listings/day} from a single IP, using adaptive throttling and rotating user-agent fingerprints to bypass rate limits and detection.}
        \resumeItemWithoutTitle{Containerized the pipeline with \textbf{Docker} and automated storage of structured data in \textbf{PostgreSQL} for downstream analytics.}
    \resumeItemListEnd

    % \resumeHeading{Column-Oriented DBMS}{Java, MiniBase}
    % \resumeItemListStart
    %     \resumeItemWithoutTitle{Enhanced MiniBase DBMS with column-oriented storage, focusing on \textbf{bitmap indexing} for efficient data retrieval.}
    %     \resumeItemWithoutTitle{Designed and implemented \textbf{standard and run-length encoded bitmap packages}, enabling dynamic operations like insertions, deletions, and retrievals.}
    %     \resumeItemWithoutTitle{Boosted query performance and storage efficiency in a columnar DBMS.}
    % \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}